\Large UC President's Postdoctoral Fellowship Research Statement: \\ \textbf{How Unique is the Solar System? Planetary Luminosities as Fingerprints for the Origins and Properties of Exoplanets}

### 2016-11-05 Postdoc Applications/uc_research_statement.tex
upd

\title{\Large UC President's Postdoctoral Fellowship Research Statement: \\
How Unique is the Solar System? Planetary Luminosities as Fingerprints for the Origins and Properties of Exoplanets}
\author{Dr. Ana-Maria Piso}

>>>>

\title{\Large UC President's Postdoctoral Fellowship Research Statement: \\
\textbf{How Unique is the Solar System? Planetary Luminosities as Fingerprints for the Origins and Properties of Exoplanets}}
\author{Dr. Ana-Maria Piso}
